---
title: "Final Project Data 608"
output: html_document
runtime: shiny
---

```{r setup environment, include=FALSE}
library(rsconnect)
library(shiny)
library(plotly)
library(ggplot2)
library(shinythemes)
library(dplyr)
library(readr)
library(reticulate)
library(rPython)
library(leaflet)
library(wesanderson)
require(shiny)
require(shinydashboard)
require(leaflet)
```

```{r deploy, echo=FALSE}

rsconnect::setAccountInfo(name='miasiracusa1',
			  token='A8DBE469F01447978C77E685D6AE43BE',
			  secret='KzPqGJEk4erc5aHrfRiyS3nrFyRzaIS0m3TR+jt1')

```

```{r import data}
#load data
calls <- read.csv("https://data.cityofnewyork.us/resource/erm2-nwe9.csv", header = TRUE)
head(calls)
```

I' will be creating've created a map which shows complaint status of calls by borough. This will hopefully be useful to different agencies to see where they have the most issues. This will hopefully shed light on if there are recurring issues in certain areas over time.

```{r map data set up}
complaint_types <- calls[,c(6,39:40)]
complaint_types <- na.omit(complaint_types)
complaint_types <- as.data.frame(complaint_types)
categories <- unique(complaint_types$complaint_type)
categories2 <- c()
for (i in 1:length(categories)) {
        categories2[i] <- toString(categories[i])}

```

Below is the map with all complaints mapped over the 5 boroughs. The complaint detail shows up when the data point is clicked.
```{r map}
# show map with complaints
cl <- colors()[1:63]

pal <- colorFactor(cl, domain = categories2)

leaflet(complaint_types) %>% addTiles() %>%
  addCircleMarkers(lng = ~longitude, lat = ~latitude, popup = ~as.character(complaint_type), radius = 4, color = ~pal(complaint_type), stroke = FALSE, fillOpacity = 0.5)
```

And below is the interactive map.
```{r map shiny app}

# Define UI
ui4 <- fluidPage(theme = shinytheme("lumen"),
  titlePanel("Complaints by type"),
  sidebarLayout(
    sidebarPanel(

      # Select borough to plot
      selectInput(inputId = "complaint_type", label = strong("complaint_type"),
                  choices = unique(complaint_types$complaint_type),
                  selected = "Street Condition")
    ),

    # Output: Description, lineplot, and reference
    mainPanel(
      leafletOutput(outputId = "mymap")
    )
  )
)

# Define server function
server4 <- function(input, output) {

  # Subset data
  complaint_map_selected <- reactive({
    req(input$complaint_type)
    complaint_types %>%
      filter(complaint_type == input$complaint_type)
  })
  

  # Create barplot object the plotOutput function is expecting
   output$mymap <- renderLeaflet({leaflet(complaint_map_selected()) %>% addTiles() %>%
     addCircleMarkers(lng = ~longitude, lat = ~latitude, radius = 4, color = ~pal(complaint_type), stroke = FALSE, fillOpacity = 0.5)
    }
  )
}

# Create Shiny object
shinyApp(ui = ui4, server = server4)

```



