---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

**Principles of Data Visualization and Introduction to ggplot2**

I have provided you with data about the 5,000 fastest growing companies in the US, as compiled by Inc. magazine. lets read this in:

```{r}

inc <- read.csv("https://raw.githubusercontent.com/charleyferrari/CUNY_DATA_608/master/module1/Data/inc5000_data.csv", header= TRUE)

```

And lets preview this data:

```{r}

head(inc)

```
```{r}

summary(inc)

```

Think a bit on what these summaries mean. Use the space below to add some more relevant non-visual exploratory information you think helps you understand this data:

```{r variable comparison}

# compare variables to one another

library(corrgram)
corrgram(inc, order=TRUE, lower.panel=panel.ellipse,
  upper.panel=panel.pts, text.panel=panel.txt,
  diag.panel=panel.minmax)

```
From the above, there appears to be a slight relationship between employees and revenue. I will explore that relationship further below:
```{r further variable comparison}

# compare employees to revenue
library(ggplot2)
plot(inc$Employees, inc$Revenue, xlab = "Employees", ylab = "Revenue")

cor(inc$Employees, inc$Revenue, use = "complete.obs")
```
As we can see, the correlation is very weak.

## Question 1

Create a graph that shows the distribution of companies in the dataset by State (ie how many are in each state). There are a lot of States, so consider which axis you should use. This visualization is ultimately going to be consumed on a 'portrait' oriented screen (ie taller than wide), which should further guide your layout choices.

```{r create states table}

# Answer Question 1 here
#load proper packages
library(dplyr)

#group states and count number in groups
states <- inc %>% 
  group_by(State) %>% 
  count(State) 

head(states)

```

```{r create table}
#load packages
library(ggplot2)

#create ggplot object
x <- ggplot(states, aes(x=reorder(State, n), y=n, fill=n))

#create bar plot
x + geom_bar(stat="identity", width=0.3, position = position_dodge(width=.5)) + coord_flip() + labs(x = "State", y = "Number of Fastest Growing Companies")
```
California has the most fast growing companies. This is probably due to the tech boom in Silicon Valley. It would be interesting to compare each states fastest growing companies by industry and see which industry dominates which states and if tech companies are doing better in certain states. This info would be helpful to people starting a company, to see where they should be located to start that company.


## Quesiton 2

Lets dig in on the state with the 3rd most companies in the data set. Imagine you work for the state and are interested in how many people are employed by companies in different industries. Create a plot that shows the average and/or median employment by industry for companies in this state (only use cases with full data, use R's `complete.cases()` function.) In addition to this, your graph should show how variable the ranges are, and you should deal with outliers.

```{r 2a}

# Answer Question 2 here
head(arrange(states, desc(n)))

#select only cases with full data
inc <- inc[complete.cases(inc),]

#select only NY companies
ny = inc %>%
  filter(State == "NY")

#check for outliers
head(arrange(ny, desc(Employees)))

#remove outliers
ny_norm = ny %>%
  filter(Employees <= 2000)


#explore NY state jobs
y <- ggplot(ny_norm, aes(reorder(Industry, Employees, mean), Employees))
y <- y + geom_boxplot() + coord_flip() + labs(x = "Industry", y = "Employees")
y
```

## Question 3

Now imagine you work for an investor and want to see which industries generate the most revenue per employee. Create a chart that makes this information clear. Once again, the distribution per industry should be shown.

```{r}

# Answer Question 3 here

#filter by industry and calculate revenue per employee
industry <- inc %>% 
  group_by(Industry) %>% 
  summarise(Revenue=sum(Revenue), Employees=sum(Employees)) %>%
  mutate(AvgRev = Revenue/Employees)

z <- ggplot(industry, aes(x=reorder(Industry, AvgRev), y=AvgRev))
z + geom_bar(stat="identity") + coord_flip() + labs(x = "Industry", y = "Number of Employees")

```

We can see here that computer hardware has the highest rate of revenue per employee.
